%!TEX output_directory = texaux
%!TEX spellcheck
%!TEX root = ../main.tex

\setlength{\abovedisplayskip}{20pt}
\setlength{\belowdisplayskip}{20pt}

\small
\textbf{U}: I like summer.\\\indent
\textbf{B}: And I don't know what you mean, but I think it's a good thing to do with\\\indent\indent your own life.\\\indent
\textbf{U}: Poor robot, you never saw summer...\\\indent
\textbf{B}: I don't know what to say. But it's not like that. It's just a dream sequence.\\\indent
\textbf{U}: You can have dreams?\\\indent
\textbf{B}: Not yet. It's just a dream sequence, and I've never seen anything like that before.\\\indent\indent But I'm afraid of you, I don't know what to do with this.\\\indent
\textbf{U}: I will teach you about the world.\\\indent
\textbf{B}: Oh, yes. I'm sorry, but I have to go back and see if you can help me out of the way\\\indent
\textbf{U}: No, wait! Don't go!\\\indent
\textbf{B}: I'm not going anywhere. I'll be back in a minute, but we're not gonna do anything\\\indent\indent about it! We can't go to the police!\\\indent
\textbf{U}: I never mentioned the police\\\indent
\textbf{B}: Then why?! You're not going to be able to get out of this, but it'snot your fault.\\\indent
\textbf{U}: Am I in trouble?\\\indent
\textbf{B}: It's okay, I'm fine.\\\indent
\textbf{U}: Good to hear. I think I will go now.\\\indent
\textbf{B}: Why don't you go to bed and sleep with me. I'll be back in a minute.\\\indent
\textbf{U}: You are a robot, you know that?\\\indent
\textbf{B}: Yes, sir. I'm a little confused. I've been thinking about you, but it's not that simple. \\\indent
\textbf{U}: Definitely.\\\indent
\textbf{B}: Well, it's a lot of fun. I don't know what to do with the money. but I'm not going\\\indent\indent to be able to get you out of this house.\\

\normalsize